\chapter{String}
    
    % \section{AHO - TBD}
    % \section{ZFUNCTION TBD}
    \section{String Hash}
    Compare two strings in $O(1)$ time, with $O(N)$ time preprocessing.
    \subsection{Simple Hash}
    \lstinputlisting{./solutions/String/StringHash.cpp}
    \subsection{Hash 2D$_{\text{ayllon}}$}
    Cuidado, a hash é dupla, pode dar TLE!
    As string são indexados de 0!
    Apenas dentro da hash que setamos para ser idexado de 1 (igual string hash normal).

    Problema resolvido: Dado duas matrizes de char, achar as posições das ocorrências da primeira matriz na segunda.
    \lstinputlisting{./solutions/String/StringHash2Dayllon.cpp}

    \subsection{Hash 2D - Gustavo}
    esse código ta horroroso
    \lstinputlisting{./solutions/String/StringHash2D.cpp}
    \subsection{Hash 2D}
    Tudo é indexado de 1
    \lstinputlisting{./solutions/String/StringHash2D-Impl2.cpp}

    \subsection{Hash with Updates}

    For this problem, the idea is that you can compare the hashes of the string and it's reversed one to discover if it is a palindrome. To do the updates, just use some data structure that allows point update and range queries. The one below uses a BIT.
    \lstinputlisting{./solutions/String/Palindrome_Queries.cpp}
    
    \section{Suffix Array}
    The key idea is to make a substring problem, into a prefix problem.
    Remember to add a '\#' at the end of the string.
    Another important fact is that $lcp(i,j) = min_{k=i}^{j-1} lcp[k]$.
    \lstinputlisting{./solutions/String/SuffixArray.cpp}
    \section{Suffix Automaton}
    The key idea is to make a substring problem, into a DAG problem.
    
    link points to the greatest suffix
    
    Most of harder problems,  you can just sort the states by len, and walk from greater to smaller
    making some updates in a dp like style.

    \lstinputlisting{./solutions/String/SuffixAutomaton.cpp}
    
    Example 1:

    You are given a string of length $n$. If all of its substrings (not necessarily distinct) are ordered lexicographically, what is the $k$-th smallest of them?

    DP to count Paths(remember its a DAG) then just do a walk. Easier version doesnt need to count repetitions, so just a path.

    \lstinputlisting{./solutions/String/SubstringOrderII.cpp}
    
    Example 2:
    
    You are given a string of length n. For every integer between 1…n you need to print the number of distinct substrings of that length.

    
    \lstinputlisting{./solutions/String/SubstringDistribution.cpp}
    
    Example 3:

    A repeating substring is a substring that occurs in two (or more) locations in the string. Your task is to find the longest repeating substring in a given string.
    
    \lstinputlisting{./solutions/String/RepeatingSubstring.cpp}
    
    \section{Suffix Tree} 
    The idea is that you transform a string problem into a tree problem, so you can use tree techniques to solve it, like LCA, Euler Tour, DP on Trees, and many others.
    
    (Original Problem SPOJ - TOP 10).
    \lstinputlisting{./solutions/String/SuffixTree.cpp}
    \section{Palindromic Tree} 
    \lstinputlisting{./solutions/String/PalinTree.cpp}
    \section{Minimal Rotation}
    Find the minimal cyclic shift of an string in O(N).
    
    \lstinputlisting{./solutions/String/SmallestCyclicShift.cpp}
    \section{Aho Corasick} 
    This aho has the shape of the Suffix Automaton, mos of things that can be done in there, can be done here as well(sort by len and do something using links).

    \lstinputlisting{./solutions/String/aho.cpp}
    
    
    